---
title: "Chapter3_sampling-map"
output: html_document
---

```{r setup, include=T}
knitr::opts_chunk$set(echo = TRUE)
```

```{r environment setup, include=F}
## R(v3.5.1 - Win)
#.libPaths(c("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_win", .libPaths("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_win")))

## R(v3.5.1 - OSX)
#.libPaths(c("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_osx", .libPaths("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_osx")))

## R(v3.5.1 - Ubuntu)
.libPaths(c("/home/mb/Dropbox/PhD Hull/PhD docs/Thesis/R_stats/rlib3.5_unix", .libPaths("/home/mb/Dropbox/PhD Hull/PhD docs/Thesis/R_stats/rlib3.5_unix")))
```

```{r directory setup, include=F}
dir()
rm(list=ls())
ls()
```

## Setting working directory and packages

The analysis was done in R (R Core Team, 2018) using the environment and packages as specified below, and in `log_map-creation.txt`.

```{r packages loading, include=T}
pack.list = c("broom","cowplot","devtools","dplyr","ggplot2","ggsn","leaflet","maps","maptools","mapview","raster","RColorBrewer","rgdal","rgeos","rworldmap","tmap")
new.packages = pack.list[!(pack.list %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, repos="https://cran.rstudio.com")
lapply(pack.list, require, character.only=T)
```

```{r session info}
sessionInfo()
```

## Plotting the map for Chapter 3 on DNA metabarcoding and MATI of invasive _D. villosus_ against non-invasive _G. zaddachi_.

```{r input data}
wb.sites = read.csv("maps/Wroxham_sites.csv")
gw.sites = read.csv("maps/Grafham_sites.csv")
rb.sites = read.csv("maps/Rockland_sites.csv")
lakes.coords = read.csv("maps/Dv_site_coords.csv")
```


Lakes coordinates include also a fourth lake which is part of this study, so it needs to be excluded from our current analysis.

```{r checking files plus removing one lake}
head(wb.sites)
head(gw.sites)
head(rb.sites)
head(lakes.coords)

# Removing not interested site
lakes.coords = lakes.coords[!(lakes.coords$ID == "Chasewater Reservoir"),]
```

Adding the labels short name

```{r}
lakes.coords$Short.Name = c("GW","WB","RB")
lakes.coords$Number = c("1","2","3")
```

Importing the lakes shapefiles to plot the sampling points

```{r loading and converting shapefiles}
uk_shape = readOGR("maps/shapefiles/GB_IRworld.shp")
# Because we have coordinates in National Grid, we convert into WGS84
wgs84 = '+proj=longlat +datum=WGS84'
uk_shape_wgs = spTransform(uk_shape, CRS(wgs84))
uk_map = fortify(uk_shape_wgs)

broads_shape = readOGR("maps/shapefiles/TG_SurfaceWater_Area.shp")
# Because we have coordinates in National Grid, we convert into WGS84
broads_wgs = spTransform(broads_shape, CRS(wgs84))
broads_map = fortify(broads_wgs)

grafham_shape = readOGR("maps/shapefiles/TL_SurfaceWater_Area.shp")
gw.sites
# Because we have coordinates in National Grid, we convert into WGS84
grafham_wgs = spTransform(grafham_shape, CRS(wgs84))
gw_map = fortify(grafham_wgs)
```

Plotting the UK map

```{r map plot}
# Saving map to file directly
png("maps/UK_map.png", width=3000, height=4000, units="px", res=300)
ggplot(uk_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_point(data=lakes.coords, aes(Longitude,Latitude), shape=c(21,22,24), fill=c("black","blue","red"), cex=3) +
  geom_text(data=lakes.coords, aes(Longitude,Latitude, label=Number), nudge_x=-0.3, cex=6) +
  coord_fixed(2) +
  theme_void() +
  north(uk_map, symbol=12, location="bottomleft")
dev.off()
```

Plotting Grafham Water

```{r grafham individual map}
png("maps/Grafham_sampling_locations.png", width=4000, height=4000, units="px", res=300)
ggplot(gw_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey60", color="black") +
  geom_point(data=gw.sites, aes(Longitude, Latitude), shape=21, fill="black", cex=4) +
  geom_text(data=gw.sites, aes(Longitude, Latitude, label=Title), nudge_x=0.001, nudge_y=0.0008, cex=7, angle=45, check_overlap=T) +
  geom_text(data=lakes.coords[grep("GW", lakes.coords$Short.Name),], aes(Longitude,Latitude, label=paste(lakes.coords[grep("GW", lakes.coords$Short.Name),"Number"],"\n",lakes.coords[grep("GW", lakes.coords$Short.Name),"ID"])), color="black", cex=15) +
  coord_cartesian(xlim=c(-0.343,-0.285), ylim=c(52.285,52.312)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=-0.342, x.max=-0.33, y.min=52.287, y.max=52.289, dist=600, dist_unit="m", st.dist=0.2, height=0.25, transform=T)
dev.off()
```

Plotting Wroxham Broad

```{r wroxham individual map}
png("maps/Wroxham_sampling_locations.png", width=4000, height=4000, units="px", res=300)
ggplot(broads_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey60", color="black") +
  geom_point(data=wb.sites, aes(Longitude, Latitude), shape=22, fill="blue", cex=4) +
  geom_text(data=wb.sites, aes(Longitude, Latitude, label=Title), nudge_x=0.0003, nudge_y=-0.0002, cex=7, angle=-45, check_overlap=T) +
  geom_text(data=lakes.coords[grep("WB", lakes.coords$Short.Name),], aes(Longitude,Latitude, label=paste(lakes.coords[grep("WB", lakes.coords$Short.Name),"Number"],"\n",lakes.coords[grep("WB", lakes.coords$Short.Name),"ID"])), color="black", cex=15) +
  coord_cartesian(xlim=c(1.409,1.423), ylim=c(52.695,52.704)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="topleft", x.min=1.409, x.max=1.41, y.min=52.701, y.max=52.7039, dist=200, dist_unit="m", st.dist=0.05, height=0.05, transform=T)
dev.off()
```

Plotting Rockland Broad

```{r rockland individual map}
png("maps/Rockland_sampling_locations.png", width=4000, height=4000, units="px", res=300)
ggplot(broads_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey60", color="black") +
  geom_point(data=rb.sites, aes(Longitude, Latitude),shape=24, fill="red", cex=4) +
  geom_text(data=rb.sites, aes(Longitude, Latitude, label=Title), nudge_x=-0.00025, nudge_y=-0.0001, cex=6, angle=45, check_overlap=T) +
  geom_text(data=lakes.coords[grep("RB", lakes.coords$Short.Name),], aes(Longitude,Latitude, label=paste(lakes.coords[grep("RB", lakes.coords$Short.Name),"Number"],"\n",lakes.coords[grep("RB", lakes.coords$Short.Name),"ID"])), color="black", cex=15) +
  coord_cartesian(xlim=c(1.4368,1.4467), ylim=c(52.5915,52.5966)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="topright", x.min=1.4457, x.max=1.4467, y.min=52.5960, y.max=52.5966, dist=100, dist_unit="m", st.dist=0.1, height=0.1, transform=T)
dev.off()
```

```{r maps multiplot for publication}
png("maps/Sites_locations.png", width=6000, height=6000, units="px", res=300)
uk = ggplot(uk_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_point(data=lakes.coords, aes(Longitude,Latitude), shape=c(21,22,24), fill=c("black","blue","red"), cex=6) +
  geom_text(data=lakes.coords, aes(Longitude,Latitude, label=Number), nudge_x=-0.6, nudge_y=0.2, cex=8, check_overlap=T) +
  geom_text(data=lakes.coords[grep("3", lakes.coords$Number),], aes(Longitude,Latitude, label=Number), nudge_x=0.6, nudge_y=-0.2, cex=8, check_overlap=T) +
  coord_fixed(2) +
  theme_void() +
  north(uk_map, symbol=12, location="bottomleft")

gw = ggplot(gw_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey60", color="black") +
  geom_point(data=gw.sites, aes(Longitude, Latitude), shape=21, fill="black", cex=7) +
  geom_text(data=gw.sites, aes(Longitude, Latitude, label=Title), nudge_x=0.003, nudge_y=0.0015, cex=10, angle=45, check_overlap=T) +
  geom_text(data=lakes.coords[grep("GW", lakes.coords$Short.Name),], aes(Longitude,Latitude, label=paste(lakes.coords[grep("GW", lakes.coords$Short.Name),"Number"],"\n",lakes.coords[grep("GW", lakes.coords$Short.Name),"ID"])), color="black", cex=15) +
  coord_cartesian(xlim=c(-0.343,-0.285), ylim=c(52.285,52.312)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=-0.3425, x.max=-0.33, y.min=52.286, y.max=52.289, dist=600, dist_unit="m", st.dist=0.2, height=0.15, transform=T) +
  theme(panel.border=element_rect(color="black", fill=NA, size=2), plot.margin=unit(c(0,0,0.25,0.25), "cm"))

wb = ggplot(broads_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey60", color="black") +
  geom_point(data=wb.sites, aes(Longitude, Latitude), shape=22, fill="blue", cex=7) +
  geom_text(data=wb.sites, aes(Longitude, Latitude, label=Title), nudge_x=0.0007, nudge_y=-0.0004, cex=10, angle=-45, check_overlap=T) +
  geom_text(data=wb.sites[grep("WB3", wb.sites$Title),], aes(Longitude, Latitude, label=Title), nudge_x=0.0001, nudge_y=-0.0005, cex=10, angle=-45, check_overlap=T) +
  geom_text(data=lakes.coords[grep("WB", lakes.coords$Short.Name),], aes(Longitude,Latitude, label=paste(lakes.coords[grep("WB", lakes.coords$Short.Name),"Number"],"\n",lakes.coords[grep("WB", lakes.coords$Short.Name),"ID"])), color="black", cex=15) +
  coord_cartesian(xlim=c(1.409,1.423), ylim=c(52.695,52.704)) +
  blank() +
  theme_void() +
  blank() +
  ggsn::scalebar(location="topleft", x.min=1.409, x.max=1.41, y.min=52.7015, y.max=52.704, dist=150, dist_unit="m", st.dist=0.05, height=0.06, transform=T) +
  theme(panel.border=element_rect(color="black", fill=NA, size=2), plot.margin=unit(c(0.25,0,0,0.25), "cm"))

rb = ggplot(broads_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey60", color="black") +
  geom_point(data=rb.sites, aes(Longitude, Latitude),shape=24, fill="red", cex=7) +
  geom_text(data=rb.sites, aes(Longitude, Latitude, label=Title), nudge_x=-0.0005, nudge_y=-0.0002, cex=10, angle=45, check_overlap=T) +
  geom_text(data=lakes.coords[grep("RB", lakes.coords$Short.Name),], aes(Longitude,Latitude, label=paste(lakes.coords[grep("RB", lakes.coords$Short.Name),"Number"],"\n",lakes.coords[grep("RB", lakes.coords$Short.Name),"ID"])), color="black", cex=15) +
  coord_cartesian(xlim=c(1.4368,1.4467), ylim=c(52.5915,52.5966)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="topright", x.min=1.4457, x.max=1.4467, y.min=52.5960, y.max=52.5966, dist=100, dist_unit="m", st.dist=0.1, height=0.15, transform=T) +
  theme(panel.border=element_rect(color="black", fill=NA, size=2), plot.margin=unit(c(0.25,0.25,0,0), "cm"))

plot_grid(uk, gw, rb, wb, nrow=2)
dev.off()
```

## WRITING LOG FILE FOR R VERSION AND SESSION INFO

```{r log creation}
sink("log_map-creation.txt")
sessionInfo()
citation()
sink()

print("end")
```