---
title: "Chapter3_sampling-map"
output: html_document
---

```{r setup, include=T}
knitr::opts_chunk$set(echo = TRUE)
```

```{r environment setup, include=F}
## R(v3.5.1 - Win)
.libPaths(c("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_win", .libPaths("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_win")))

## R(v3.5.1 - OSX)
#.libPaths(c("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_osx", .libPaths("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_osx")))

## R(v3.5.1 - Ubuntu)
#.libPaths(c("/home/mb/Dropbox/PhD Hull/PhD docs/Thesis/R_stats/rlib3.5_unix", .libPaths("/home/mb/Dropbox/PhD Hull/PhD docs/Thesis/R_stats/rlib3.5_unix")))
```

```{r directory setup, include=F}
dir()
#rm(list=ls())
ls()
```

## Setting working directory and packages

The analysis was done in R (R Core Team, 2018) using the environment and packages as specified below, and in `log_map-creation.txt`.

```{r packages loading, include=T}
pack.list = c("broom","devtools","dplyr","ggplot2","ggsn","leaflet","maps","maptools","mapview","raster","RColorBrewer","rgdal","rgeos","rworldmap","tmap")
new.packages = pack.list[!(pack.list %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, repos="https://cran.rstudio.com")
lapply(pack.list, require, character.only=T)
```

## Plotting the map for Chapter 3 on DNA metabarcoding and MATI of invasive _D. villosus_ against non-invasive _G. zaddachi_.

```{r input data}
wb.sites = read.csv("maps/Wroxham_sites.csv")
gw.sites = read.csv("maps/Grafham_sites.csv")
rb.sites = read.csv("maps/Rockland_sites.csv")
lakes.coords = read.csv("maps/Dv_site_coords.csv")
```


Lakes coordinates include also a fourth lake which is part of this study, so it needs to be excluded from our current analysis.

```{r checking files plus removing one lake}
head(wb.sites)
head(gw.sites)
head(rb.sites)
head(lakes.coords)

# Removing not interested site
lakes.coords = lakes.coords[!(lakes.coords$ID == "Chasewater Reservoir"),]
```

Adding the labels short name

```{r}
lakes.coords$Short.Name = c("GW","WB","RB")
```


```{r map plot}
uk_shape = readOGR("maps/shapefiles/GB_IRworld.shp")

# Because we have coordinates in National Grid, we convert into WGS84
wgs84 = '+proj=longlat +datum=WGS84'
uk_shape_wgs = spTransform(uk_shape, CRS(wgs84))

uk_map = fortify(uk_shape_wgs)

# Saving map to file directly
png("maps/Site_locations.png", width=600, height=820, units="px")
ggplot(uk_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_point(data=lakes.coords, aes(Longitude,Latitude), color="black", cex=3) +
  geom_text(data=lakes.coords, aes(Longitude,Latitude, label=Short.Name), nudge_x=-0.4, cex=4) +
  coord_fixed(2) +
  theme_void()
dev.off()

## FROM HERE!
```

Importing the lakes shapefiles to plot the sampling points

```{r wroxham shapefile}
wroxham_shape = readOGR("maps/shapefiles/TG_SurfaceWater_Area.shp")

# Because we have coordinates in National Grid, we convert into WGS84
wroxham_wgs = spTransform(wroxham_shape, CRS(wgs84))
wb_map = fortify(wroxham_wgs)

png("maps/Wroxham_sampling_locations.png", width=600, height=820, units="px")
ggplot(wb_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_point(data=wb.sites, aes(Longitude, Latitude), color="red", cex=3) +
  geom_text(data=wb.sites, aes(Longitude, Latitude, label=Title), nudge_x=-0.001, nudge_y=0.0001, cex=4) +
  xlim(1.40,1.429) + ylim(52.694,52.705) +
  coord_fixed(2) +
  theme_void()
dev.off()
```

```{r grafham shapefile}
grafham_shape = readOGR("maps/shapefiles/TL_SurfaceWater_Area.shp")
gw.sites
# Because we have coordinates in National Grid, we convert into WGS84
grafham_wgs = spTransform(grafham_shape, CRS(wgs84))
gw_map = fortify(grafham_wgs)

png("maps/Grafham_sampling_locations.png", width=820, height=600, units="px")
ggplot(gw_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_point(data=gw.sites, aes(Longitude, Latitude), color="red", cex=3) +
  geom_text(data=gw.sites, aes(Longitude, Latitude, label=Title), nudge_x=-0.001, nudge_y=0.001, cex=4) +
  xlim(-0.35,-0.28) + ylim(52.278,52.315) +
  coord_fixed(2) +
  theme_void()
dev.off()
```

```{r rockland shapefile}
rockland_shape = readOGR("maps/shapefiles/TG_SurfaceWater_Area.shp")

# Because we have coordinates in National Grid, we convert into WGS84
rockland_wgs = spTransform(rockland_shape, CRS(wgs84))
rb_map = fortify(rockland_wgs)

png("maps/Rockland_sampling_locations.png", width=820, height=600, units="px")
ggplot(rb_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_point(data=rb.sites, aes(Longitude, Latitude), color="red", cex=3) +
  geom_text(data=rb.sites, aes(Longitude, Latitude, label=Title), nudge_x=-0.001, nudge_y=0.0001, cex=4) +
  xlim(1.4364,1.4470) + ylim(52.5914,52.5972) +
  coord_fixed(2) +
  theme_void()
dev.off()
```

## WRITING LOG FILE FOR R VERSION AND SESSION INFO

```{r log creation}
sink("log_map-creation.txt")
sessionInfo()
citation()
sink()

print("END")
```